---
title: "HW4_code"
author: "Hengchang Hu"
date: "10/2/18"
output:
  pdf_document: default
  html_document: default
---
#### Chapter 2.2
&nbsp;

#### (a)

```{r}
indicators <- read.table("C:/Users/hugo1/Documents/MA575/HW4/indicators.txt", header = TRUE) 
# import the dataset

OLS_priceloan <- lm(PriceChange~LoanPaymentsOverdue, indicators) 
# get the least square model

esti_beta1_pl <- coef(summary(OLS_priceloan))[, "Estimate"]["LoanPaymentsOverdue"][[1]]

print(paste("The estimation of beta_1 is ", esti_beta1_pl))
# show estimation value of beta_1

std_beta1_pl <- coef(summary(OLS_priceloan))[, "Std. Error"]["LoanPaymentsOverdue"][[1]] 

print(paste("The Standard error of beta_1 is ", std_beta1_pl))
# show standard error value of beta_1

print(paste("The 95% CI of beta_1 is [", esti_beta1_pl - 
              qt(0.975,16) * std_beta1_pl, esti_beta1_pl
            + qt(0.975,16) * std_beta1_pl, "]"))
# 95% confidence interval of beta_1
```

### From above we can tell that there is evidence of a significant negative linear association.
&nbsp;

####(b)

```{r}
newdata <- list("LoanPaymentsOverdue" = 4) # type in newdata

esti_pl_4 <- predict(OLS_priceloan, newdata)[[1]] # estimation value

print(paste("When X = 4, E(Y|X) = ", esti_pl_4)) # show estimation value

S_pl <- summary(OLS_priceloan)$sigma # get the estimate of sigma

SXX_pl <- (S_pl / std_beta1_pl) ^ 2 # get SXX

lowerbound_pl <- esti_pl_4 - qt(0.975, 16) * S_pl * sqrt(1 / 18 + 
    (4 - mean(indicators["LoanPaymentsOverdue"][,1])) ^ 2 / SXX_pl)
# get the lower bound of 95% CI for E(Y|X=4)

upperbound_pl <- esti_pl_4 + qt(0.975, 16) * S_pl * sqrt(1 / 18 + 
    (4 - mean(indicators["LoanPaymentsOverdue"][,1])) ^ 2 / SXX_pl)
# upper bound

print(paste("95% CI for E(Y|X=4) is [", lowerbound_pl, upperbound_pl, "]"))
# 95% CI for E(Y|X=4)
```

### From above we can tell that 0% is not in the 95% CI for E(Y|X=4), so it is not a feasible value.
&nbsp;

#### Chapter 2.3
&nbsp;

#### (a)

#### Through the output of R, $\hat{\beta_0}$ is 0.6417099, $se(\hat{\beta_0})$ is 0.1222707, Degree of Freedom is 28. Therefore, the 95% CI for $\beta_0$ is [`r 0.6417099 - qt(0.975, 28) * 0.1222707`, `r 0.6417099 + qt(0.975, 28) * 0.1222707`].
&nbsp;

#### (b)

#### From the output of R, we can know that $\hat{\beta_1} = 0.0112916$, and the $se(\hat{\beta_1}) = 0.0008184$. Since the statistics $T = \frac{(\hat{\beta_1} - \beta_1)}{se(\hat{\beta_1})}$ = `r (0.0112916 - 0.01) / 0.0008184`, and the acceptance region is $\big[t(0.025, n-2), t(0.975, n-2)\big]$ = [`r qt(0.025, 28)`, `r qt(0.975, 28)`]. Therefore the T statistics fall into acceptance region, can not reject the null hypothesis.
&nbsp;

#### (c)

#### When $X=130$, $E(Y|X=130) = 0.6417099 + 0.0112916 \times 130$ = `r 0.6417099 + 0.0112916 * 130`. And the 95% CI for $E(Y|X=130)% is [`r 2.1096179 - qt(0.975, 28) * 0.3298 * sqrt(1/30)`, `r 2.1096179 + qt(0.975, 28) * 0.3298 * sqrt(1/30)`]
&nbsp;

#### Chapter 2.6
&nbsp;

#### (a)

\begin{equation*}
\begin{split}
(y_i - \hat{y_i}) &= y_i - \hat{\beta_0} - \hat{\beta_1} x_i \\
&= y_i - (\bar{y} - \hat{\beta_1} \bar{x}) - \hat{\beta_1} x_i \\
&= (y_i - \bar{y}) - \hat{\beta_1} (x_i - \bar{x})
\end{split}
\end{equation*}

&nbsp;

#### (b)

\begin{equation*}
\begin{split}
(\hat{y_i} - \bar{y}) &= \hat{\beta_0} + \hat{\beta_1} x_i - \bar{y} \\
&= \bar{y} - \hat{\beta_1} \bar{x} + \hat{\beta_1} x_i - \bar{y} \\
&= \hat{\beta_1}(x_i - \bar{x})
\end{split}
\end{equation*}

&nbsp;

#### (c)

\begin{equation*}
\begin{split}
\sum_{i=1}^{n}(y_i - \hat{y_i})(\hat{y_i} - \bar{y}) &= \sum_{i=1}^{n}\big[(y_i - \bar{y}) - \hat{\beta_1} (x_i - \bar{x})\big] \hat{\beta_1}(x_i - \bar{x}) \\
&= \hat{\beta_1} \Big(\sum_{i=1}^{n} (y_i - \bar{y})(x_i - \bar{x}) - \hat{\beta_1} \sum_{i=1}^{n} (x_i - \bar{x})^2 \Big) \\
&= \hat{\beta_1} \Big(SXY - \frac{SXY}{SXX} SXX\Big) \\
&= 0
\end{split}
\end{equation*}






