---
title: "MA575 Lab6"
author: "Shuqiang Chen, Hengchang Hu, Haikuo Lu, Chi Chen, Shreya Gupta, Azar Ghahari"
date: "10.24.2018"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r,echo = TRUE}
# 1. Choose the response variable (Y) and one covariate (X). 
#Please put some though for your response and covariate variable selection.
# import dataset day.csv
BikeSharingInDay <- read.csv(file = "C:/Users/hugo1/Documents/ma575/Proj/day.csv")

# Sneak peak at the data
head(BikeSharingInDay)

# choose counts of total rental bikes as response variable (Y)
# hypothesis: temp(X1),atemp(X2),hum(X3),windspeed(X4),holiday(X5),weathersit(X6),year(X7) have impact on counts of total rental bikes(Y)
cnt <- BikeSharingInDay$cnt

# choose covariate (X1~X7)
temp <- BikeSharingInDay$temp
atemp <- BikeSharingInDay$atemp
hum <- BikeSharingInDay$hum
windspeed <- BikeSharingInDay$windspeed
holiday <- BikeSharingInDay$holiday
weathersit <- BikeSharingInDay$weathersit
year <- BikeSharingInDay$yr

```
### We choose these four covariates (temp,atemp,hum,windspeed) because they are all numeric variables and easy to interpret. And we choose other three covariates (holiday,weathersit,year) because we thought it may affect the using of bikes.

* * *

```{r,echo=TRUE}
# 2. Plot Y VS. X1-x4 (i.e. a scatterplot) from the data.
# Plot scatter matrix 
pairs(~cnt+temp+atemp+hum+windspeed,gap=0.4)
```



```{r,echo=TRUE}
m.mls <- lm(cnt ~ temp + atemp + hum + windspeed + holiday + weathersit + year)
summary(m.mls)

# correlation matrix
X <- cbind(cnt, temp, atemp, hum, windspeed, holiday, weathersit, year)
c <- cor(X)
round(c,3)
```
### We delete 'atemp' variable because it is not that signficant and this variable is highly correlated with 'temp' variable. 
* * * 

```{r,echo=TRUE}
# 3. Perform MLR using R on your response (Y) and covariates (X1,X2, ..Xr) .

m.mls <- lm(cnt ~ temp + hum + windspeed + holiday + weathersit + year)
summary(m.mls)


```
### 4.In the output of this MLR, we can see that except 'hum' is significant under 0.05 significant level other covariates are all significant under 0.001 significant level. 
* * *

```{r,echo=TRUE}
# 5.Standard Residuals
StanResMLS <- rstandard(m.mls)
par(mfrow=c(1,1))
plot(cnt,StanResMLS,xlab="cnt", ylab="Standardized Residuals", col="green")
abline(h=2,lty=2)
abline(h=-2,lty=2)

```
### From the plot, we think it is a good model.