---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

#### 1. Choose the response variable (Y) and one covariate (X) & Put thought for your response and covariate variable selection.

```{r, echo = TRUE}
BikeSharingInDay <- read.csv(file = "C:/Users/hugo1/Documents/MA575/Proj/day.csv")
# import dataset day.csv

casual <- as.numeric(unlist(BikeSharingInDay['casual']))
# choose counts of casual users as response variable (Y)

atemp <- as.numeric(unlist(BikeSharingInDay['atemp']))
# choose normalized temperature in Celsius as covariate (X)
```

* * *

#### 2. Plot Y vx X (i.e. a scatterplot) from the data.

```{r, echo = TRUE}
plot(atemp, casual, xlab = 'Feeling Temperature', ylab = 'Counts of Casual Users')
# scatterplot of casual vs atemp
```

* * *

#### 3&4. Perform OLS using R on your response and covariate & Submit the output from R of OLS (coefficient estimate, t values, p values) and interpret the results.

```{r, echo = TRUE}
OLS_Casual_Atemp <- lm(casual~atemp)
# OLS on casual vs atemp

summary(OLS_Casual_Atemp)
# summary of this OLS
```

* * *

#### 5. Plot also Y vs X for your choice of data set and overlay on your plot the linear regression fit obtained from R.

```{r, echo = TRUE}
plot(atemp, casual , xlab = 'Feeling Temperature', ylab = 'Counts of Casual Users')
# scatterplot

abline(lsfit(atemp, casual), col = 'red')
# linear regression fit obtained from R
```

